\chapter*{Acknowledgements}

I want to direct my gratitude to my supervisor João Mendes Moreira for all the
time we spend trying to mine the knowledge about data mining on my raw rock
mind, without him none of this would be possible. I want to direct the same
gratitude to the company supervisor João Azevedo, for all the insights about the
online advertising market ecosystem. To my co-supervisor a special thanks to the
inception of failure that you implanted on my brain which help me get to this
point.

To all my friends on FEUP with whom I spend allmost every waking hour of my life
for the past 5 years. A giant thanks to all of you, specially, Ana Ferreira,
Bruno Maia, Daniel Freitas, Marco Amador, Margarida Pereira, Maria Barreira,
 Pedro Oliveira, Renato Rodrigues, Renato Marinho, Tiago Mota and Tiago Rodrigues. All of you had
a special role in my life on the past years. A special acknowledge for
Diogo Teixeira and Clara Sacramento was to be made, thank you for all the great
times we spent at NIAEFEUP, without you I would not be
able to complete this report.

To my parents António and Josefina, thank you for everything that you did so I
could become the person I am today. I hope I could live to fulfill all the
expectations you have for me.

Maria Soutelo, thank you for every hour you had to spend without me, thank you
for every hour you had been kept wake so I could work, thank for all the help!
Without you I would not be writing this right now. Thank you for making me the
happiest person on the face of this planet.

\vspace{10mm}
\flushleft{Pedro Borges}
