\chapter{Problem Description}\label{chap:chap3}

\section*{}

The online advertising market is huge and its size has been increasing in money,
campaigns and users. Both platforms that sell and buy space for ad placement
want to understand what is their value and more important, what will be their
value in the future. In both cases this value is mostly constrain by campaigns
and users that are target for their campaigns.

Our goal is to forecast the availability of the users in the future so we can
simulate the value of future campaigns over them.

Since we do not know which characteristics the future campaigns will have, there
is the need to forecast every detail available on the impressions, in order to
obtain the correct values when the queries are executed over the generated data.

So main goal is to be able to generate a dataset able to be used on a campaign
simulator, so we must me able to predict the values with the maximum detail
possible.

This simulator needs to have available every detail possible about every
impression in order to identify which impressions are compatible with each
campaign. The result would be express by number of impressions per campaign and
users target by every campaign, over time.

The approach should also be independent on any parameter other than the
date and the user id of the impression, since that would be feed to this
approach can have multiple sources and each source stores only the relevant
parameters to then. The approach should be able to generate data for any source
with any parameters, based only on historical information.

In form of conclusion, the main objectives are:
\begin{itemize}
\item Correctly predict volumes of activity on an ad network for a given time in
  the future based only past data;
\item Fill the volumes with impressions, with the maximum detail possible, to be
  able to use the obtained result on a simulator.
\end{itemize}
